Satellite Alignments in the Local Group

### 2017-07-06 paper/ms.tex
cosmic web

\newcommand{\Mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\dm}{{\ifmmode{{\Delta M}}\else{$\Delta M$}\fi}}
\newcommand{\dlm}{{\ifmmode{{\Delta \log M}}\else{$\Delta \log M$}\fi}}
\newcommand{\focc}{{\ifmmode{{f_{\rm occ}}}\else{${f_{\rm occ}}$}\fi}}
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\tol}{Tololo 1214-277}
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vek}[1]{\bm{#1}}
%\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}

@@

\subsection{Sample Selection}

We select all halos with maximum circular velocities in the
range 150 km s$^{-1}$ $<V_{\rm max}<$ 350 km s$^{1}$.
We exclude sub-halos from this selection.
From this set we construct a sample of pairs as follows.
For each halo $A$ we find its closest halo $B$, if halo $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's distance.
We exclude the pairs that are closer than
There are $53$ pairs with those conditions in the simulation.

We extract from the simulation spheres of $2$ \hMpc  in radius around
the pair's center of mass. 
We use this information to exclude all the pairs that have separations
smaller than the sum of their virial radii, i.e. we exclude
interacting pairs. 
This reduces to $49$ the number of pairs in the sample.

We count the number of galaxies with $M_V<-9$ inside the virial
radius of each halo, including the central galaxy.
We only keep pairs where both halos have 5 bright galaxies at least. 
This reduces the sample to $24$ pairs. 
We call this sample the Full Sample.

From the Full Sample we build a second sample based on the pairs' kinematics. 
Figure \ref{fig:samples} shows the co-moving separation and relative
speed between the two halos in the pair.
The stars in the Figure represent the pairs with a separation in the
range $0.75\hMpc <R_{AB}< 1.50\hMpc$ and relative velocity in the
range $V_{AB}>100$ km s$^{-1}$, which are close to the Local Group
Observed values.
We call this sample the LG Sample.

The number of pairs in the Full Sample is consistent with previous
calculations. 
\cite{ForeroRomero2013} performed a study of the LG kinematics using a
cosmological N-body simulation as a benchmark. 
In their study, using criteria similar to ours to define the Full
Sample, they found 1923 pairs in a volume of $250^3$ $h^{-3}$
Mpc$^{3}$. 
With the same number density we expect to find $52$ pairs in the
volume of the Illustris simulation, which is very close to the actual
number of $49$ pairs.

In the same study they found 158 pairs with broad kinematic
characteristics, similar to the definition of our LG sample. 
This represents a reduction of a factor of $12$ from their General
Sample. 
With those numbers in mind we would expect to keep at least $4$ pairs
in the Illustris volume. 
Given that our conditions are slightly more relaxed (we do not ask for
isolation criteria from massive halos) we end up with a larger sample
size, but still consistent with the fact that LG-like pairs are
scarce.  
%no me es muy claro este ultimo parrafo. En nuestros samples pasamos de 49 a 24 (o sea se redujo en un factor 2 en vez de un factor 12)

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{v_r_pairs.pdf}
\caption{Halo pair samples used in this paper located in the
  plane of relative co-moving velocity $V_{AB}$ versus relative
  distance $R_{AB}$ between the two halos in the pair.
  The R\&V sample is the closest to the separation and kinematic
  conditions observed in the Local Group.}
\label{fig:samples}
\end{figure}

>>>>

\newcommand{\Mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\dm}{{\ifmmode{{\Delta M}}\else{$\Delta M$}\fi}}
\newcommand{\dlm}{{\ifmmode{{\Delta \log M}}\else{$\Delta \log M$}\fi}}
\newcommand{\focc}{{\ifmmode{{f_{\rm occ}}}\else{${f_{\rm occ}}$}\fi}}
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\tol}{Tololo 1214-277}
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vek}[1]{\bm{#1}}
%\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}

@@

%no me es muy claro este ultimo parrafo. En nuestros samples pasamos de 49 a 24 (o sea se redujo en un factor 2 en vez de un factor 12)

### 2017-07-06 paper/paper.tex
new titles
cosmic web

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellite alignments]{
Local Group Satellite Alignments in a Cosmological Context}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\section{Data and Algorithms}
\label{sec:NumericalSetup}

\subsection{Data from the Illustris Project}

@@

\subsection{Galaxy Pair Selection}

@@

@@

\end{document}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellite alignments]{Satellite Alignments in the Local Group}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\section{Local Group Analogues in the Illustris Simulation}
\label{sec:NumericalSetup}

@@

\subsection{Sample Selection: Local Group Analogues}

@@

\section{Cosmic Web Calculations}

We also find the place IS and LGS pairs into the cosmic web as quantified by the deformation tensor
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor 
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that follows the
Poisson equation $\nabla^2\phi=-\delta$, with $\delta$ the DM matter
overdentisy, and the $r_i$ coordinates correspond to a cartesian
system with $i=1,2,3$.

This tensor can be diagonalized.
Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
define the degree and direction of stability around the neighborhood
where the tensor is computed. 
This allows the classification of that region either as a peak,
filament, sheet or voids in the case of three, two, one or zero
eigenvalues larger than a given threshold $\lambda_{\rm th}$.

In this study we compute these eigenvalues and eigenvectors over the
dark matter component of the Illustris-3 simulation on a cubic mesh of
$74$ cells on a side. 
This resolution corresponds to $\sim 1$ \hMpc.
We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
scheme, then smooth the density field with a gaussian window with a
physical scale equal to the cell size.

We choose this interpolation and smoothing scale for two reasons.
First, because it corresponds to the typical pair separation in our
sample, making each halo in the pair share the same environment.
Second, because it allows a direct comparison with previous results in
the literature that used the same methodology to quantify the cosmic
web environment for Local Group pairs in a cosmological context
\citep{ForeroRomero2013,2015ApJ...799...45F}.

@@

%% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P
\end{document}
